Case study validations of automatic bullet matching

### 2018-11-19 index.Rmd
shapes added

aucpic <- aucs %>%
  ggplot(aes(x = auc, y = measurenum, colour = studyg)) +
  facet_grid(studyg~.) +
  geom_segment(aes(x = auc_ci_low, xend = auc_ci_low, y = measurenum - .125, yend = measurenum + .125), size = 1) + 
  geom_segment(aes(x = auc_ci_high, xend = auc_ci_high, y = measurenum - .125, yend = measurenum + .125), size = 1) + 
  geom_segment(aes(x=auc_ci_low, xend=auc_ci_high, y = measurenum, yend = measurenum, linetype=measure), size=1) +
  geom_point(size=3) +
  theme_bw() +
  xlab("AUC and 95% confidence intervals") +
  xlim(c(0.5, 1)) +
  scale_y_continuous("", breaks = unique(aucs$measurenum), labels = unique(aucs$measurechar)) + 
  scale_colour_manual("Study", values = c("#fe9929", "#aa0000",
                                         "#74a9cf", "#2b8cbe", "#045a8d"),
                        guide = FALSE) +
  # theme(legend.position = "bottom",
  #       legend.key.width = unit(1.5, "cm")) +
  scale_linetype_manual("Measure", values = c(3,1,2), guide = F)

@@

```{r eer, fig.width=7, fig.height = 4, fig.cap="Equal Error (in Percent)  and corresponding thresholds for all measures (RF score, Cross-correlation and CMS) under all five (sub-)studies. CMS has an equal error threshold of 2 for all studies. CMS is signifcantly worse than both Cross-correlation and the RF score. At best, Cross-correlation and RF score have equal errors for land-to-land comparison of around 5\\%.", out.width = '.8\\textwidth'}
aucs %>% 
  mutate(
    eer = 100*eer
  ) %>%
  gather(eer_thresh, value, eer, threshold) %>%
  filter(!(measure=="CMS" & eer_thresh=="threshold")) %>%
  mutate(
    eer_thresh = factor(eer_thresh, labels=c("Equal Error (in Percent)", "Threshold for Equal Error"))
  ) %>%
  ggplot(aes(y = studyg, x = value, colour=measure, shape = measure)) + 
  geom_point(size = 4) +theme_bw() +
  xlab("Equal Error (in Percent, left) and corresponding thresholds (right)") +
  ylab("") +
  scale_color_brewer(palette = "Set2") +
  scale_shape_discrete(solid = F) + 
  theme(legend.position = "bottom") +
  facet_grid(.~eer_thresh, scales="free") +
  xlim(c(0, NA))
```

>>>>

aucpic <- aucs %>%
  ggplot(aes(x = auc, y = measurenum, colour = studyg)) +
  facet_grid(studyg~.) +
  geom_segment(aes(x = auc_ci_low, xend = auc_ci_low, y = measurenum - .125, yend = measurenum + .125), size = 1) + 
  geom_segment(aes(x = auc_ci_high, xend = auc_ci_high, y = measurenum - .125, yend = measurenum + .125), size = 1) + 
  geom_segment(aes(x=auc_ci_low, xend=auc_ci_high, y = measurenum, yend = measurenum, linetype=measure), size=1) +
  geom_point(size=3.5, aes(shape = measure)) +
  theme_bw() +
  xlab("AUC and 95% confidence intervals") +
  xlim(c(0.5, 1)) +
  scale_y_continuous("", breaks = unique(aucs$measurenum), labels = unique(aucs$measurechar)) + 
  scale_colour_manual("Study", values = c("#fe9929", "#aa0000",
                                         "#74a9cf", "#2b8cbe", "#045a8d"),
                        guide = FALSE) +
  # theme(legend.position = "bottom",
  #       legend.key.width = unit(1.5, "cm")) +
  scale_linetype_manual("Measure", values = c(3,1,2), guide = F) +
  scale_shape_discrete(guide=F)

@@

```{r eer, fig.width=7, fig.height = 4, fig.cap="Equal Error (in Percent)  and corresponding thresholds for all measures (RF score, Cross-correlation and CMS) under all five (sub-)studies. CMS has an equal error threshold of 2 for all studies. CMS is signifcantly worse than both Cross-correlation and the RF score. At best, Cross-correlation and RF score have equal errors for land-to-land comparison of around 5\\%.", out.width = '.8\\textwidth'}
aucs %>% 
  mutate(
    eer = 100*eer
  ) %>%
  gather(eer_thresh, value, eer, threshold) %>%
  filter(!(measure=="CMS" & eer_thresh=="threshold")) %>%
  mutate(
    eer_thresh = factor(eer_thresh, labels=c("Equal Error (in Percent)", "Threshold for Equal Error"))
  ) %>%
  ggplot(aes(y = studyg, x = value, colour=measure, shape = measure)) + 
  geom_point(size = 3.5) +
  theme_bw() +
  xlab("Equal Error (in Percent, left) and corresponding thresholds (right)") +
  ylab("") +
  scale_color_brewer(palette = "Set2") +
  scale_shape_discrete(solid = F) + 
  theme(legend.position = "bottom") +
  facet_grid(.~eer_thresh, scales="free") +
  xlim(c(0, NA))
```
